On exponential sums arising from the classical doubling method

### 2025-03-04 paper.tex
g-1 => 1-g

Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(g-\IdentityMatrix{k}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{k}\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.

@@

\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
	We have the identity
	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proposition}
\begin{proof}
	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$. Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	Changing variables $h \mapsto X^{-1} h$, we get
	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proof}

We now use this to compute $\dblJacobiSum{\tau}{\chi}$. We have that $$\dblJacobiSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\dblJacobiSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

@@

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
\chi\left(\detQuadratic\left(g - \idmap_{\hermitianSpace}\right)\right) & \text{if }\detQuadratic\left(g - \idmap_{\hermitianSpace}\right) \ne 0\\
0 & \text{otherwise,}
\end{dcases}$$
is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$.

@@

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
	Hence, \begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
	\begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.

	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(a - \IdentityMatrix{k}\right) \det\left(\involution{\left(a - \IdentityMatrix{k}\right)}\right) \detQuadratic\left( g' - \idmap_{\hermitianSpace'}\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}

@@

The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right).$$
Let us rewrite this as
$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$, this becomes
$$q^{-k} \alpha\left(-1\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
Hence, we have the identity
$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$

\subsubsection{Split torus computation II}
We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$. Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$. Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(\minusInvolution{x} - 1\right)\right).$$
This can be rewritten as
$$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
By the previous section, this equals
\begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
\end{equation}

@@

Let $\theta \colon \NormOneGroup{2m} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\involutionPlusOne{\chi} \ne 1$. Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right).$$

@@

As usual, we rewrite the sum as follows
$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$

>>>>

Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(\IdentityMatrix{k}-g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}-g\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.

@@

\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
	We have the identity
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proposition}
\begin{proof}
	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det\left(-h\right)\right).$$
	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$. Thus	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	Changing variables $h \mapsto X^{-1} h$, we get
	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proof}

We now use this to compute $\dblJacobiSum{\tau}{\chi}$. We have that $$\dblJacobiSum{\tau}{\chi} = \chi\left(-1\right)^k q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(-y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\dblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

@@

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} - g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} - g\right) \ne 0\\
0 & \text{otherwise,}
\end{dcases}$$
is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$.

@@

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(-\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
	Hence, \begin{align*}
		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
	\begin{align*}
		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.

	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} - p\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} - a\right) \det\left(\involution{\left(\IdentityMatrix{k} - a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} - g'\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}

@@

The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1-x\right)\right).$$
Let us rewrite this as
$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\left(-1\right)^k\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$, this becomes
$$q^{-k} \alpha\left(-1\right) \chi\left(-1\right)^k \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
Hence, we have the identity
$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \chi\left(-1\right)^k \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$

\subsubsection{Split torus computation II}
We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$. Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$. Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 - x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 - \minusInvolution{x}\right)\right).$$
This can be rewritten as
$$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(1 - x\right)\right).$$
By the previous section, this equals
\begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
\end{equation}

@@

Let $\theta \colon \NormOneGroup{2m} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\involutionPlusOne{\chi} \ne 1$. Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(1 - x\right)\right).$$

@@

As usual, we rewrite the sum as follows
$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(-y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
